Factors determining how catchments respond to forest cover change. Re-analysing global data sets.

### 2022-02-02 paper/Forest_and_Water/Forest_and_Water.Rmd
Merge branch 'main' of https://github.com/WillemVervoort/Forest_and_water

```{r, echo = F, warning = F, message=F, eval =F}
# plot to show the difference
png("Increase_decrease.png", width = 2500, height = 1800, res = 300)
All_data2 %>%
  ggplot(aes(DeltaF_perc_pos,DeltaQf_perc, colour = Forest_Sign)) + 
  geom_point() +  
  facet_wrap(~Forest_Sign, ncol=1, scales = "free") + 
  theme_bw() + 
    theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.2)),
        legend.text = element_text(size = rel(1.2)),
        legend.title = element_text(size = rel(1.2)),
        strip.text = element_text(size = rel(1.5))) + 
  scale_colour_manual(name = "Forest change direction", 
                      values = c("decrease" = "red","increase" = "blue")) +
  xlab("Change in forest cover %") + ylab("Change in flow (Qf) %")
dev.off()

>>>>

```{r, echo = F, warning = F, message=F, eval =F}
# plot to show the difference
png("Increase_decrease.png", width = 2500, height = 1800, res = 300)
All_data2 %>%
  ggplot(aes(DeltaF_perc_pos,DeltaQf_perc, colour = Forest_Sign)) + 
  geom_point() +  
  facet_wrap(~Forest_Sign, ncol=1, scales = "free") + 
  theme_bw() + 
    theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.2)),
        legend.text = element_text(size = rel(1.2)),
        legend.title = element_text(size = rel(1.2)),
        strip.text = element_text(size = rel(1.5))) + 
  scale_colour_manual(name = "Forest change direction", 
                      values = c("Decrease" = "red","Increase" = "blue")) +
  xlab("Change in forest cover %") + ylab("Change in flow (Qf) %")
dev.off()
